Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex
Fix raisebox

We show that we can extend our system to new features by first introducing a simple
example model, and then moving to a more realistic model with multiple new features:
callee-save registers, argument passing on the stack, and tail-call elimination, simply
by refining a few definitions in (1). This becomes the model that we validate.
In \cref{app:ptr}, we extend the model further with arbitrary sharing of memory-safe
pointers. Our criteria in (3) cover a total of five core requirements:
\(\wbcf\), caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
callee integrity (\(\clei\)), and callee confidentiality (\(\clec\)).
They are related to one another as seen in
\cref{fig:propertydiagram}:\leo{is this supposed to be \cref{tab:props}?} \(\clei\) subsumes \(\clrc\) and \(\clec\) subsumes
\(\clri\), but otherwise the properties are orthogonal and can be taken piecemeal
according to the needs of a system.

@@

\begin{figure}
  \centering
  \[
  \stackrel{\texttt{res}}{\figfourbox[0]}
  \stackrel{\texttt{sens}}{\figfourbox[0]}
  \stackrel{\texttt{sec}}{\figfourbox[5]}
  \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
  %
  \[\big\Downarrow\]
  %
  \[
  \stackrel{\texttt{res}}{\figfourbox[0]}
  \stackrel{\texttt{sens}}{\genbox{20px}{red!50}{\bf 42}}
  \stackrel{\texttt{sec}}{\figfourbox[5]}
  \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
  %
  \[\overbrace{
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\genbox{20px}{\leftvariant}{\bf 42}}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}
    \hspace{1cm}
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\genbox{20px}{\rightvariant}{\bf 0}}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}}\]
  \[\stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{5}} \hspace{0.5cm}
  \raisebox{\height}{\not\approx}
  \hspace{0.5cm}
  \stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{1}}\]
  \caption{Integrity Violation}
  \label{fig:variant}
\end{figure}

@@

\begin{figure}
    \centering
    \[
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\figfourbox[0]}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
    %
    \[\overbrace{
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}}
    \]
    \[\raisebox{.5\height}{\Bigg\Downarrow} \hspace{1cm}
    \stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{5}} \hspace{0.5cm}
    \raisebox{\height}{\not\approx}
    \hspace{0.5cm}
    \stackrel{\(\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{4}} \hspace{1cm}
    \raisebox{.5\height}{\Bigg\Downarrow}\]
    \[
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}
    \]

>>>>

We show that we can extend our system to new features by first introducing a simple
example model, and then moving to a more realistic model with multiple new features:
callee-save registers, argument passing on the stack, and tail-call elimination, simply
by refining a few definitions in (1). This becomes the model that we validate.
In \cref{app:ptr}, we extend the model further with arbitrary sharing of memory-safe
pointers. Our criteria in (3) cover a total of five core requirements:
\(\wbcf\), caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
\(\clei\) subsumes \(\clrc\) and \(\clec\) subsumes
\(\clri\), but otherwise the properties are orthogonal and can be taken piecemeal
according to the needs of a system.

@@

\begin{figure}
  \centering
  \[
  \stackrel{\texttt{res}}{\figfourbox[0]}
  \stackrel{\texttt{sens}}{\figfourbox[0]}
  \stackrel{\texttt{sec}}{\figfourbox[5]}
  \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
  %
  \[\big\Downarrow\]
  %
  \[
  \stackrel{\texttt{res}}{\figfourbox[0]}
  \stackrel{\texttt{sens}}{\genbox{20px}{red!50}{\bf 42}}
  \stackrel{\texttt{sec}}{\figfourbox[5]}
  \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
  %
  \[\overbrace{
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\genbox{20px}{\leftvariant}{\bf 42}}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}
    \hspace{1cm}
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\genbox{20px}{\rightvariant}{\bf 0}}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}}\]
  \[\stackrel{\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{5}} \hspace{0.5cm}
  %\raisebox{\height}{\not\approx}
  \hspace{0.5cm}
  \stackrel{\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{1}}\]
  \caption{Integrity Violation}
  \label{fig:variant}
\end{figure}

@@

\begin{figure}
    \centering
    \[
    \stackrel{\texttt{res}}{\figfourbox[0]}
    \stackrel{\texttt{sens}}{\figfourbox[0]}
    \stackrel{\texttt{sec}}{\figfourbox[5]}
    \stackrel{\texttt{ra}}{\figfourbox[0]\figfourbox[0]}\]
    %
    \[\overbrace{
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}}
    \]
    \[%\raisebox{.5\height}{\Bigg\Downarrow} \hspace{1cm}
    \stackrel{\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{5}} \hspace{0.5cm}
    %\raisebox{\height}{\not\approx}
    \hspace{0.5cm}
    \stackrel{\hookrightarrow \mathtt{out}}{\genbox{20px}{white}{4}} \hspace{1cm}
    %    \raisebox{.5\height}{\Bigg\Downarrow}
    \]
    \[
    \stackrel{\texttt{res}}{\leftbox[0]}
    \stackrel{\texttt{sens}}{\leftbox[0]}
    \stackrel{\texttt{sec}}{\leftbox[5]}
    \stackrel{\texttt{ra}}{\leftbox[0]\leftbox[0]}
    \hspace{1cm}
    %
    \stackrel{\texttt{res}}{\rightbox[2]}
    \stackrel{\texttt{sens}}{\rightbox[3]}
    \stackrel{\texttt{sec}}{\rightbox[4]}
    \stackrel{\texttt{ra}}{\rightbox[5]\rightbox[6]}
    \]
